A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-01-01 main.tex
Updates from Overleaf

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Histories, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

@@

>>>>

Head and neck squamous cell carcinoma (\acrshort{hnscc}), including oral, oropharyngeal, and hypopharyngeal origin, is the fourth leading cancer causes of death for males in Taiwan\cite{MOHW_death2017}. The age-standardized incidence rate of \acrshort{hnscc} in males is 42.43 per 100,000 persons\cite{MOHW_incidence2018}. 
% chemotherapy => systemic therapy
The treatment strategies of \acrshort{hnscc} are surgery alone, systemic therapy with concurrent radiation therapy (systemic therapy/\acrshort{rt}), or surgery with adjuvant systemic therapy/\acrshort{rt} (according to \acrlong{nccn}, \acrshort{nccn} Clinical Practice Guidelines in \acrshort{hnscc}, Version 2.2020)\cite{Pfister2020a}. Despite the improvement in those interventions, the survival of \acrshort{hnscc} has improved only marginally over the past decade worldwide\cite{hpa2019}. The critical advancement of targeted therapy and immuno-oncology should benefit from emerging prognostic biomarkers, which guide the development of modern systemic therapy.

%% TP53 gene => p53 protein; mutation of TP53
Accumulative knowledge showed that some biomarkers have prognostic significance in \acrshort{hnscc}. For example, node-negative \acrshort{hnscc} patients with p53 overexpression were found to have lower survival\cite{DeVicente2004}.
Overexpression of \acrfull{hif}-1 alpha\cite{Aebersold2001} or Ki-67\cite{Couture2002} was found to be correlated with poor response to radiotherapy of \acrshort{hnscc}. The \acrfull{egfr}\cite{O-Charoenrat2000}\cite{Bentzen2005} and \acrfull{mmp}\cite{Harrington2017} were found to be over-expressed to promote invasion and metastasis of \acrshort{hnscc}.
From 2000 to 2006, the anti-\acrshort{egfr} antibody-drug (cetuximab) has been developed and combined with radiotherapy, known as bio-\acrshort{rt}, to increase survival of unresectable locoregionally advanced disease\cite{Bonner2006a}.
The systemic therapy of cetuximab plus platinum-fluorouracil chemotherapy (EXTREME regimen) improves overall survival when given as first-line treatment in patients with recurrent or metastatic \acrshort{hnscc}\cite{Vermorken2008}\cite{Rivera2009}. It was approved by the \acrshort{us} \acrfull{fda} in 2008. In advance, the bio-\acrshort{rt} could have proceeded with \acrfull{tpf} induction chemotherapy to overcome the radio-resistance of \acrshort{hnscc}\cite{Blanchard2013}.

However, Rampias and his colleagues suggested \acrfull{hras} mutations could mediate cetuximab resistance in systemic therapy of \acrshort{hnscc} via the \acrshort{egfr}/\acrfull{ras}/\acrfull{erk} signaling pathway\cite{Rampias2014}.
After that, the \acrshort{egfr} \acrfull{tki} was introduced to help cetuximab in 2018. The anti-tumor activity was observed in a phase 1 trial for \acrshort{hnscc} patients using cetuximab and afatinib, a \acrshort{tki} of \acrshort{egfr}, \acrfull{her}2, and \acrshort{her}4\cite{Gazzah2018}. Other \acrshort{egfr} \acrshort{tki}, such as gefitinib, erlotinib, osimertinib, were also developed to treat advanced \acrshort{hnscc}.
Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.

Until the immuno-oncology era, \acrfull{ici} was introduced since 2014 for treating \acrshort{hnscc}\cite{Seiwert2014}\cite{Swanson2015}.
The \acrshort{ici} works on immune checkpoint molecules, which including \acrfull{pd1}, \acrfull{ctla4}, \acrfull{tim3}, \acrfull{lag3}, \acrfull{tigit}, \acrfull{gitr} and \acrfull{vista}\cite{Mei2020}.
The \acrshort{us} \acrshort{fda} has approved the anti-\acrshort{pd1} agents, pembrolizumab, and nivolumab, as a monotherapy for the platinum-treated patients of recurrent or metastatic \acrshort{hnscc}\cite{Cramer2019}. However, because of the complexity of immune-tumor interaction, \acrshort{ici} has not to guarantee the response to \acrfull{pdl1} expressed \acrshort{hnscc}\cite{Swanson2015}.
According to the phase 3 KEYNOTE-048 study, \acrshort{pdl1} is a validated biomarker used in clinical guidance for candidate selection of pembrolizumab\cite{Burtness2019}\cite{Gavrielatou2020}.

In our previous proteomic study in 2017, \acrfull{tmsb4x} was reported to be related to tumor growth and metastasis of \acrshort{hnscc}\cite{Chi2017}. It was also found by the subsequent investigations that \acrshort{tmsb4x} engaged in tumor aggressiveness through \acrfull{emt} on pancreatic\cite{Zhang2008}, gastric\cite{Ryu2012}, colorectal\cite{Gemoll2015}, lung\cite{Huang2016}, ovarian\cite{Chu2019} and melanoma\cite{Makowiecka2019} cancers. Thus, it might be suggested that \acrshort{tmsb4x}  is possible for tumor type-agnostic therapy\cite{Yan2018} as a common biomarker crossing several types of cancer.
%TMSB4X proteins regulate intracellular signal transduction and has been proved to overexpress in various cancers, including colorectal, lung, gastric, pancreatic, and squamous cell cancers.\cite{Chi2017}
% https://doi.org/10.1038/s41598-017-09539-w

In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis, so far.
Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

In our approach, this article described a comprehensive workflow implemented in the R script, which runs on the Rstudio server. Its functions include data retrieving and pre-processing, feature selection, cutoff mining engine, Kaplan-Meier survival analysis, Cox proportional hazard modeling, and biomarker selection.
Using this workflow on the \acrshort{tcga} \acrshort{hnscc} cohort, the 20,500 human protein-coding genes were scanned. The analysis workflow is shown in Figure \ref{fig:figure1}.
%We found that the surgical margin status and tobacco exposure are independent risk factors of patient survival. 
%Our findings also suggested several candidate biomarkers are associated with the prognosis of overall survival (OS) under optimal cutoff point with significant P-value. Those genes may be potential therapeutic targets of HNSCC.

\section{Results}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
